\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-10-15 src/tex/ms.tex
Adding a bit more text

% Author list
\author{Adam Coogan} \UdeM \Mila
\author{Thomas D.~P.~Edwards} \OKC \NORDITA
\author{Daniel Foreman-Mackey} \CCA
\author{Maximiliano Isi} \CCA
\author{Kaze W.~K.~Wong} \CCA
\author{Aaron Zimmerman} \CGP

@@

\subsection{Effectualness Calculations}
\label{sec:effectualness}

>>>>

% Author list
\author{Adam Coogan} \UdeM \Mila
\author{Thomas D.~P.~Edwards} \OKC \NORDITA
\author{Daniel Foreman-Mackey} \CCA
\author{Maximiliano Isi} \CCA
\author{Kelvin Lam} \CCA
\author{Kaze W.~K.~Wong} \CCA
\author{Aaron Zimmerman} \CGP

@@

\te{Kelvin should add stuff here}

\subsection{Fisher Forecasting}
\label{subsec:hmc}

Forecasting the sensitivity of future experiments is an essential task in GW science.
Due to its theoretical simplicity and its evaluation speed, the Fisher matrix formalism is commonly deployed to estimate how well the a particular binary system's parameters can be measure.
The Fisher matrix approach is built around the assumption of a Gaussian likelihood.
Although in practice this assumption is often violated in for real GW datasets, the results obtained using a Fisher analysis can provide quick and useful diagnotistics in evaluating sensitivities for a variety of models.

Computing the Fisher matrix requires one to evaluate derivatives of the likelihhood...
